---
title: "Homework 25"
output: html_notebook
---



#This is a draft of all work done in Biostats Homeowork 25. I will be going through the second half of Chapter 5 Getting Started with R

Linear Models

As usual we clear everything and add our packages
```{r}
rm (list = ls())
library(dplyr)
library(ggplot2)
library(here)
```

#Making sure I know where I am
Importing the Data
```{r}
here::here()
```

## Importing Data using here package
```{r}
here()
plant_gr <- read.csv(here("Data", "plant.growth.rate.csv"))
```


#Ok data is now imported with the here package so lets check it out

```{r}
glimpse(plant_gr)
```
#alright pretty standard stuff, two variables so lets make a quick scatter plot

```{r}
View(plant_gr)
```


Scatter Plot
```{r}
ggplot(plant_gr,
aes (x = soil.moisture.content, y = plant.growth.rate)) +
geom_point() +
ylab("Plant Growth Rate (mm/week)") +
theme_bw()
```
#For whatever this isnt working so I am going to rename it and try it again.

```{r}
plant_gr %>% 
    rename("SMC" = "soil.moisture.content")
plant_gr %>%
  rename("PGR" = "plant.growth.rate")
```
#This is saying that plant.growth.rate does not exist, weird

#Importing a different dataset called plant.growth.rate.witherror
```{r}
plant_gr_er <- read_csv(here("Data", "plant.growth.rate.witherror.csv"))
```

#Trying again with a new data set plant_gr_er
Scatter Plot
```{r}
ggplot(plant_gr_er,
aes (x = soil.moisture.content, y = plant.growth.rate)) +
geom_point() +
ylab("Plant Growth Rate (mm/week)") +
theme_bw()
```

#ok so I went back and imported my data differently, hopefully this will work
```{r}
ggplot(plant_gr,
aes(x = soil.moisture.content, y = plant.growth.rate)) +
geom_point() +
ylab("Plant Growth Rate (mm/week)") + theme_bw()
```
#Finally ok so I need to be using the here package differently I think, still confused but worked it out lets move on 

LM Model
#Trying this from the book 
```{r}
model_pgr <- lm(plant.growth.rate ~ soil.moisture.content,
data = plant_gr)
```
#looks good, fit the linear model 


Using Auto Pilot 
#importing ggfortify 
```{r}
library(ggfortify)
autoplot(model_pgr, smooth.colour = NA)
```
#The line represents residual errors around the fitted line
#Top left. This panel is about the ‘systematic part’ of the model
#Top right. This evaluates the assumption of normality of the residuals
#Bottom left. This evaluates the assumption of equal variance
#Bottom right. This evaluates leverage, a tool not only to detect influential data points, ones that move the gradient more than might be expected, but also to detect outliers

#That was a lot but I feel this is very very important 


Making an ANOVA

```{r}
anova(model_pgr)
```
#F value = 156,08 and a pvalue = 2.2e-16. This is small and thus significant.

Summary of Model PGR
```{r}
summary(model_pgr)
```
#The estimates provided in the summary table (the first column) correspond to the estimates, in a linear regression, of the intercept and slope associated with the explanatory variable


The final step - translating the model we have fitted back onto our figure of the raw data

```{r}
ggplot(plant_gr, aes(x = soil.moisture.content,
y = plant.growth.rate)) +
geom_point() +
geom_smooth(method = 'lm') +
ylab("Plant Growth Rate (mm/week)") +
theme_bw()
```
#The smooth part is what shoves the linear model into the figure

Analysis of variance : the one-way ANOVA

#very similar to linear regression model but with catagorical data

## Importing Data using here package
```{r}
here()
daphnia <- read.csv(here("Data", "Daphniagrowth.csv"))
```

Checking out the Data
```{r}
glimpse(daphnia)
```

#Box and whisker plot to make a figure before jumping into the data
```{r}
ggplot(daphnia, aes(x = parasite, y = growth.rate)) + geom_boxplot() +
theme_bw()+ coord_flip()
```

#So apparently this has a coord flip but I do not see a difference 
```{r}
ggplot(daphnia, aes(x = parasite, y = growth.rate)) +
geom_boxplot() +
theme_bw() +
coord_flip()
```

Construct the ANOVA

```{r}
model_grow <- lm(growth.rate ~ parasite, data = daphnia)
```

Check the assumptions 

```{r}
autoplot(model_grow, smooth.colour = NA)
```
#Same as the last but different test

MAKING AN INFERENCE FROM A ONE-WAY ANOVA

```{r}
anova(model_grow)
```
#low P-value again 

Summary
```{r}
summary(model_grow)
```
Different from Linear Regression Model. 
#So, in an ANOVA framework, we can assume that the word ‘(Intercept)’represents the first level of the alphabetically ordered treatment levels.. So, in the summary table, the numbers associated with each parasite are differences between growth rates associated with that parasite and the control. This is why they are all negative. These negative distances, or contrasts, are the lengths of the black lines 


The mean growth rates
```{r}
sumDat<-daphnia %>%
group_by(parasite) %>%
summarise(meanGR = mean(growth.rate))
```

#This was a whole bunch of information but it was also very helpful. Hopefully it can all stick 
