---
title: "Using dplyr to fix mistakes"
author: "Drew"
date: "10/3/2022"
output: html_document
---


In this assignment I will be experimenting with using stringAsFactors = True, and the use of the Unique() function to see how it summarizes the data

Clear R's brain and turn on the dplyr and here packages
```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(here)
```

#Importing the Data without stringAsFactors = True,   

#Code 1
```{r}
DF <- read.csv(here("Data", "drug_resistance.csv"))
summary(DF)

```


#Importing the Data with stringAsFactors = True

#Code 2
```{r}
DF <- read.csv(here("Data", "drug_resistance.csv"), stringsAsFactors = TRUE)
summary(DF)
```

#The difference in the variables is that when you run stringAsFactors = True, it uses the treatment and tech.name data as factors with certain levels, and when you dont run stringAsFactors = True, they are run as characters.

#The summary for Code 1 only includes the number of length of characters, while code 2 includes the names of all the factors, and the number of each individual factor in the data set



