---
title: "Homework24draft"
output: html_notebook
---

#This is a draft of all work done in Biostats Homeowork 24. I will be going through the first half of Chapter 5 

As usual we clear everything and add our packages
```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(here)
```

Importing the Data
```{r}
here::here()
```
#I know I should be using the here package but I forgot how it works, I think this is right though.
```{r}
ozone <- read_csv(here("Data", "ozone.csv"))
Ladybird <- read_csv(here("Data", "ladybirds.csv"))
```

#Ok I added the wrong data table now I put in ladybirds_morph_colour.csv
```{r}
Lady <- read_csv(here("Data", "ladybirds_morph_colour.csv"))
```
#ok sweet

IT LOOKS LIKE YOU ARE USING THE GUI TO LOAD THE DATA. LEARN TO LOAD THE DATA WITHOUT THE GUI. YOUR CODE DOES NOT LOAD THE DATA AS WRITTEN BECAUSE YOU ARE USING READ_CSV AND NOT READ.CSV.

Now we begin the chapter

Now we are gonna checkout the data we just added
```{r}
glimpse(Lady)
```
#alright pretty neat and tiddy data, not bad at all, decent consistency but somethings arent completley identitcal

Lets summarize the data shall we
```{r}
totals <- Lady %>%
group_by(Habitat, morph_colour) %>%
summarise(total.number = sum(number))
```
#Just following along in the book but this sumarizes the data and can be seen in the environment panel

Histogram
```{r}
ggplot(totals, aes(x = Habitat, y = total.number,
fill = morph_colour)) +
geom_bar(stat = 'identity', position = 'dodge')
```
#Histogram looks good but the color key is wrong lets fix that

```{r}
ggplot(totals, aes(x = Habitat, y = total.number,
fill = morph_colour)) +
geom_bar(stat = 'identity', position = 'dodge') +
scale_fill_manual(values = c(black = "black", red = "red"))
```
#nice we totally fixed that problem by "values = c(black= "black", red = "red")"

Making a x^2 test feat. chisq.test(). 

#Still reading but this did not work 
```{r}
chisq.test(Lady).
```


#This didnt work either, time to start reading again 
```{r}
chisq.test(Lady)
```

Summarize the data with a matrix
```{r}
lady.mat <- xtabs(number ~ Habitat + morph_colour,
data = Lady)
```
#Im pretty sure this is what that is doing because it gave us a Value in the Environment window

Now the x^2 test 
```{r}
chisq.test(lady.mat)
```
#This is actually really sweet, also I am writing more stuff which is much better

OK, SO YOU HAVE A TEST. HOW DO YOU INTERPRET THE RESULTS? WHY DID YOU HAVE TO CREATE A MATRIX? PUT MORE OF YOUR THOUGHTS INTO THE RMD FILE.

# ‘Yates’ continuity correction refers to a little adjustment of the x2 test that makes it a bitmore reliable when the counts are small. 

Assigning the values to a name
```{r}
lady.chi <- chisq.test(lady.mat)
names(lady.chi)
```
#what good is this value? What can we do with this?

Now we move to Ozone

#look at the Ozone Data
```{r}
glimpse(Ozone)
```

#What is wrong with this?
```{r}
ggplot(Ozone, aes(x = Ozone)) +
geom_histogram(binwidth = 10) +
facet_wrap(~ Garden.location, ncol = 1) +
theme_bw()
```

#I cant get this to work so I am going to move on. Its werid because its identical to the book.
```{r}
ggplot()Ozone, aes(x = Ozone)) +
geom_histogram(binwidth = 10) +
facet_wrap(~ Garden.location, ncol = 1) +
theme_bw()
```

YOUR PROBLEM IS THAT YOUR DATAFRAME IS CALLED OZONE WITH A LOWERCASE O BUT YOU HAVE IT WITH CAPITAL O

Now we do the t.test
#cross our fingers 

```{r}
t.test(Ozone ~ Garden.location, data = Ozone)
```
#Damn

#It didnt work because I couldnt do the last step, curses

#let me try something
```{r}
glimpse(ozone)
```
#I went back and remade my Data "ozone" and not "Ozone" but alas it did not work

```{r}
ggplot(ozone, aes(x = Ozone)) +
geom_histogram(binwidth = 10) +
facet_wrap(~ Garden.location, ncol = 1) +
theme_bw()
```
OK CAN YOU GUESSTIMATE THE MEANS HERE BEFORE YOU RUN THE TEST?

T.test 2.0

```{r}
t.test(Ozone ~ Garden.location, data = ozone)
```

#Ok same error message as before, time to ask for help

IT WORKED FOR ME - NOT SURE WHAT THE ERROR MESSAGE WAS

#This would have been the T-test summary, although it did not work by any means because I could not do the T.test.
```{r}
var.test(Ozone ~ Garden.location, data = ozone)
```

#Alright we will get them next time

YOU SHOULD BE PUTTING MORE OF THE "WHY" IN YOUR CODE, AS WELL AS THE INTERPRETATIONS FOR THE OUTPUT THAT THE BOOK EXPLAINS.
